---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
library(rio)
library(dplyr)
library(ggplot2)
```

```{r}
df = import("egypt_wave3.csv")
```

# Subsetting relevant columns

```{r}
df = df %>%
        select(ee1, ee2, ti1, ti2, sd1)
head(df)
```
# ee1 update

```{r}
unique(df$ee1)
```

* In the context of Egypt, respondents only selected the answer choices shown above

```{r}
df <- df %>%
  mutate(EconomyToday = ifelse(ee1 %in% c(-1, 0, 7, 8, 9), NA, ee1))
unique(df$EconomyToday)
```

* Only the number 8 option takes on NA

# ee2 update

```{r}
unique(df$ee2)
```

```{r}
df <- df %>%
  mutate(EconomyPast = ifelse(ee2 %in% c(-1, 0, 7, 8, 9), NA, ee2))
unique(df$EconomyPast)
```

* Options 8 and 9 become NAs

# ti1 question not asked in Arab Barometer

```{r}
unique(df$ti1)
```

* Look at codebook under the Trust in Institutions tab, ARAB4 and LATINO15 have no data on this which explains why it's all missing

# ti2 update

```{r}
unique(df$ti2)
```

```{r}
df <- df %>%
  mutate(TrustInGovt = ifelse(ti2 %in% c(-1, 0, 7, 8, 9), NA, ti2))
unique(df$TrustInGovt)
```

* Options 8 and 9 become NAs

# sc1 update

```{r}
unique(df$sc1)
```

* contains nothing that needs to be changed to NA

```{r}
df <- df %>%
  mutate(TrustInPeople = ifelse(sc1 %in% c(-1, 0, 7, 8, 9), NA, sc1))
unique(df$TrustInPeople)
```

summary of the data
```{r}
summary(df)
```

Variable distribution for ee1
```{r}
ggplot(df, aes(x = ee1)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(title = "Distribution of ee1", x = "ee1", y = "Frequency")

```
variable distrivution for ee2
```{r}
ggplot(df, aes(x = ee2)) +
  geom_histogram(binwidth = 1, fill = "pink", color = "black") +
  labs(title = "Distribution of ee2", x = "ee2", y = "Frequency")
```
variable distribution for ti1
```{r}
ggplot(df, aes(x = ti1)) +
  geom_histogram(binwidth = 1, fill = "red", color = "black") +
  labs(title = "Distribution of ti1", x = "ti1", y = "Frequency")
```
variable distribution for ti2
```{r}
ggplot(df, aes(x = ti2)) +
  geom_histogram(binwidth = 1, fill = "green", color = "black") +
  labs(title = "Distribution of ti2", x = "ti2", y = "Frequency")
```
variable distibution for sc1
```{r}
ggplot(df, aes(x = sc1)) +
  geom_histogram(binwidth = 1, fill = "green", color = "black") +
  labs(title = "Distribution of sc1", x = "sc1", y = "Frequency")
```
Test Hypothesis 1
```{r}
table(df$ti2)
```

